The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-20 src/static/authors.tex
Update src/static/authors.tex
Co-authored-by: P. L. Lim <2090236+pllim@users.noreply.github.com>

\author[0000-0001-6637-6922]{James~Tocknell}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0003-0353-9741]{Jaime~A.~Alvarado-Montes}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0002-1852-9653]{Gabriel~I~Perren}
\affiliation{Instituto de Astrof\'isica de La Plata (IALP-CONICET), La Plata, Argentina}

@@

\author[0000-0001-5185-9876]{Lee~R.~Spitler}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics, Macquarie University, Sydney, NSW 2109, Australia}

>>>>

\author[0000-0001-6637-6922]{James~Tocknell}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0003-0353-9741]{Jaime~A.~Alvarado-Montes}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0002-1852-9653]{Gabriel~I~Perren}
\affiliation{Instituto de Astrof\'isica de La Plata, IALP (CONICET-UNLP), 1900 La Plata, Argentina}

@@

\author[0000-0001-5185-9876]{Lee~R.~Spitler}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics, Macquarie University, Sydney, NSW 2109, Australia}
